---
title: "Quality of US Hospitals by 30-day Death Rates"
output: html_notebook
---

This notebook explores how to read real world data and execute filtering on it.
The data is a snapshot of the "Hospital Compare" database. The activities
in the notebook are generally guided by the Week 4 assignment "Assignment 3" of
the "Introduction to R Programming" course on Coursera. Use the included
`Hosptial_Revised_Flatfiles.pdf` to understand the CSV table
`outcome-of-care-measures.csv`, which is **entry 19** on page 17.


```{r}
if (!require(testthat)) install.packages('testthat')
library(testthat)

setwd("~/R/IntroR/Week4/Assignment3")

source("best.R")
source("rankhospital.R")
source("rankall.R")
```

# Part 1: Plot the 30-day mortality rates for heart attack

```{r}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
head(outcome)
```

```{r}
colnames(outcome)
```


```{r}
as_numeric_cols <- c(11)
outcome[, as_numeric_cols] <- as.numeric(outcome[, as_numeric_cols])
hist(outcome[, 11], xlab=colnames(outcome)[11])
```

# Part 2: Finding the best hospital in a state

```{r}
expect_true(best("TX", "heart attack") == "CYPRESS FAIRBANKS MEDICAL CENTER")
expect_true(best("TX", "heart failure") == "FORT DUNCAN MEDICAL CENTER")
expect_true(best("MD", "heart attack") == "JOHNS HOPKINS HOSPITAL, THE")
expect_true(best("MD", "pneumonia") == "GREATER BALTIMORE MEDICAL CENTER")
expect_error(best("BB", "heart attack"))
expect_error(best("NY", "hert attack"))
```

# Part 3: Ranking hospitals by outcome in a state

```{r}
expect_true(rankhospital("TX", "heart failure", 4) == "DETAR HOSPITAL NAVARRO")
expect_true(rankhospital("MD", "heart attack", "worst") == "HARFORD MEMORIAL HOSPITAL")
expect_true(is.na(rankhospital("MN", "heart attack", 5000)))
```

# Part 4: Ranking hospitals in all states

```{r}
head(rankall("heart attack", 20), 10)
```

```{r}
tail(rankall("pneumonia", "worst"), 3)
```

```{r}
tail(rankall("heart failure"), 10)
```

# Quiz

## Q1:

```{r}
suppressWarnings(best("SC", "heart attack"))
```

## Q2:

```{r}
suppressWarnings(best("NY", "pneumonia"))
```

## Q3:

```{r}
suppressWarnings(best("AK", "pneumonia"))
```

## Q4:

```{r}
suppressWarnings(rankhospital("NC", "heart attack", "worst"))
```

## Q5:

```{r}
suppressWarnings(rankhospital("WA", "heart attack", 7))
```

## Q6:

```{r}
suppressWarnings(rankhospital("TX", "pneumonia", 10))
```

## Q7:

```{r}
suppressWarnings(rankhospital("NY", "heart attack", 7))
```

## Q8:

```{r}
suppressWarnings(r <- rankall("heart attack", 4))
as.character(subset(r, state == "HI")$hospital)
```

## Q9:

```{r}
suppressWarnings(r <- rankall("pneumonia", "worst"))
as.character(subset(r, state == "NJ")$hospital)
```

## Q10:

```{r}
suppressWarnings(r <- rankall("heart failure", 10))
as.character(subset(r, state == "NV")$hospital)
```
